Papers

### 2025-01-02 papers.qmd
added paper
update for 2025
fix spaces

## 2024
N. Winovich, Nick, L. Moynihan, O. Abdelrahman, R. West, S. Dauphin, **J. D. Tucker**, G. Huerta, K. Potter, R. Forrest, C. Phillips, and M. Ebeida, "VoroClust: Scalable Clustering for Remote Sensing", *IEEE Transactions on Geoscience and Remote Sensing*, submitted, 2024.

J.E. Borgert, J. Hannig, **J.D. Tucker**, L. Arbeeva, A. N. Buck, Y. M. Golightly, S. P. Messier, A. E. Nelson, and J.S. Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, submitted, 2024. [arxiv preprint](https://arxiv.org/abs/2409.13938)

A. Heiskala, **J. D. Tucker**, P. Choudhary, R. Nedelec, J. Ronkainen, O. Sarala, M. Järvelin, M. J. Sillanpääm, and Sylvain Sebert, "Timing based clustering of childhood BMI trajectories reveal differential maturational patterns; Study in the Northern Finland Birth Cohorts 1966 and 1986", *International Journal of Obesity*, accepted, 2024.

@@

D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, in revision, 2024. [arxiv preprint](https://arxiv.org/abs/2308.05915)

>>>>

## 2025

## 2024
K. Goode, **J. D. Tucker**, D. Ries, and H. Hoffman, "An Explainable Pipeline for Machine Learning with Functional Data", *Annals of Applied Statistics*, submitted, 2024.

N. Winovich, Nick, L. Moynihan, O. Abdelrahman, R. West, S. Dauphin, **J. D. Tucker**, G. Huerta, K. Potter, R. Forrest, C. Phillips, and M. Ebeida, "VoroClust: Scalable Clustering for Remote Sensing", *IEEE Transactions on Geoscience and Remote Sensing*, submitted, 2024.

J. E. Borgert, J. Hannig, **J. D. Tucker**, L. Arbeeva, A. N. Buck, Y. M. Golightly, S. P. Messier, A. E. Nelson, and J. S. Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, submitted, 2024. [arxiv preprint](https://arxiv.org/abs/2409.13938)

A. Heiskala, **J. D. Tucker**, P. Choudhary, R. Nedelec, J. Ronkainen, O. Sarala, M. Järvelin, M. J. Sillanpääm, and S. Sebert, "Timing based clustering of childhood BMI trajectories reveal differential maturational patterns; Study in the Northern Finland Birth Cohorts 1966 and 1986", *International Journal of Obesity*, accepted, 2024.

@@
